The DAO Hack

### 2019-01-07 paper/paper.tex
changed fonds + dao

An investment fund is a fund where investors can invest money.
With the money the fund manager manages which shares to buy/sell when based on the defined goals, risks and other factors of the specific fund.
The gain can then be payed out to the investors and the loss will shrink the fund.

@@

The DAO is like an investment fund running without any hierarchical management.
Investors (ethereum addresses) can exchange ether for DAO tokens (the DAOs currency) in the initial phase.

The initial phase defines some starting properties of the DAO like the minimum ether required to successfully build the DAO.
Instead of a fund manager like in the investment fund each investor gets voting rights based on the invested money.
With this voting rights one can vote where the money should be invested.
To propose an investment an investor can create a proposal.
The proposal contains the recipient (an ethereum address) of the investment, the amount in ether, the voting deadline, among other properties.
When a proposal is accepted, which means more than a given amount of votes voted yes the DAO executes the proposal, meaning it transfers the money to the recipient.
To prevent proposal spams the proposal creator has to pay a small fee for each proposal he creates, which he gets back iff the proposal is accepted.

But how do we prevent illegal proposals or proposals that pays out all the investment to a bad person who has more then 50\% of the voting rights?
For this reasons each DAO has the curator (an ethereum address), a person who can accept or reject proposals before the voting window gets opened.
This curator is also defined in the initial phase.

The curator principle removes a bit of the non hierarchical management.
To give the investors more flexibility they can change the curator at any time for any reason.
For this purpose one has to create a special proposal called a split proposal.
The creator defines a new curator in this proposal and the old curator can not reject it.
The DAO automatically starts the voting period.

After this period the DAO is split in two.
All investors voting yes are now in the new DAO and their investment is transfered to it while the others stay in the old one.

>>>>

An investment fund is used to invest money. A investor can give money to a fond which will in turn invest the money by buying shares and other investment opportunities. Usually a fond will have a big diversification between their investments, often bigger than any single entity could achieve. A fond usually has some guidlines on how to invest the money based on risk and other factors. Those factors mostly differ a lot between fonds. As an example there are fonds that focus on the swiss market, or on the telecomunication market world wide.

The fond usually has someone in charge of the investments called fonds manager. He has the power to invest the money. Additionally to shares fonds also invest in proposals. A proposal is generated by companies where they offer investment opportunities for a specific project or program. The fond manager then bids on the proposals he thinks will be profitable.

The fonds manager also generates a report about how well the fond did. Based on that shares of the fond can be sold at a profit.

@@

The DAO is like an investment fund running without any hierarchical management.
Investors (ethereum addresses) can exchange ether for DAO tokens (the DAOs currency) in a phase called initial phase. In the initial phase some starting properties are defined for the DAO like minimum ether required to successfully fund the DAO. It's like a kickstarter campaign, where people have to invest money to fund a project.

In the DAO there is no fund manager, instead each investor has a voting right based on the amount of tokens he holds. This is comparable to share holder meetings of a company. There the company invites all the investors (share holders) and they can vote with their shares. This is very impractical in the physical world as it is very hard to get all the investors together to vote for proposals.

In the DAO this is way easier. As everything is digital votes can be held with large enough time frames and every investor can vote with a signed message on the blockchain. This way every proposal can be voted on by all the investors and they can directly influence where their money will be invested.

A proposal can be created by any investor. It contains recipient of the investment, the amount of ether, the voting deadlines and other properties. For a proposal to be accepted it needs to have a given amount of Yes votes, it is executed, which means that the ether is sent to the recipient. To create a proposal the investor has to pay a fee, which will be refunded if it is accepted.

To prevent malicious proposals there is an entity called curator. He can decline proposals before they go to a vote. This is necessary if a investor with a lot of voting power (>50\%) should create a proposal to send all the funds to his address. This curator is defined in the initial phase.

This curator obviously goes against the non-hierarchical management rule but he is necessary to protect against malicious proposals. Any investor can split off the main DAO into a new Sub DAO with a new curator. This split is a proposal as well which the curator can't block. After the voting period, which is smaller than the normal voting period, all investors who voted yes can split off the old DAO and join the new one. This way all investors are protected, even those who have a minority.
